\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-12 arch.tex
- rewrote the topic of the synchronization flaw figure

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\columnwidth]{figs/synch-relation}
  \caption{Ilustration of the synchronization in a reactor. The
    reactor receive new observations when they are produced by the
    owner(s) of its internal timlines. Meanwhile at every tick it
    identifies the potential flaw of himself not having identify its
    state for the current tick and will try to resolve it according to
    its model $\mathcal{M}$} 
  \label{fig:synch:flaw}
\end{figure}

>>>>

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\columnwidth]{figs/synch-relation}
  \caption{Ilustration of the synchronization flaws in a reactor. The
    reactor receive new observations when they are produced by the
    owner(s) of its internal timelines. The line after the last token
    of each timeline represent the domain of possible values for the
    end of this token. At every tick $\tau$ the reactor needs to
    integrate the {\em External} state information it received and --
    based on its model $\mathcal{M}$ -- resolve its {\em Internal}
    state that will then be provided by the architecture to other
    reactors using these state variables.}
  \label{fig:synch:flaw}
\end{figure}
